---
title: "JavaMOP"
author: "Rodrigo Bonifácio et al."
date: "1/26/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd(".")
library(sqldf)
library(xtable)
```

## Load the datasets

```{r load}
bench03mop <- read.csv("mop-report.csv", head=T, sep=",")
bench03cc  <- read.csv("CogniCrypt-Report.csv", head=T, sep=",")
bench03cg <- read.csv("CryptoGuard-Report.csv", head=T, sep=",")

gt <- read.csv("gt.csv", head=T, sep=",")

gt <- na.omit(gt)

nrow(bench03mop)
colnames(bench03mop)

nrow(bench03cc)
colnames(bench03cc)

nrow(bench03cg)
colnames(bench03cg)

colnames(gt)
nrow(gt)
```

### Filter out irrelevant warnings for the stud

This is necessary because we have enriched the test cases for more complete scenarios, instead of just instantiating cryptographic primitives and then doing nothing with them. To solve this issue, we introduce the usege of Keys. 

```{r}
bench03mop <- sqldf("select * from bench03mop where spec != 'KeyGeneratorSpec'")
nrow(bench03mop)

bench03cc <- sqldf("select * from bench03cc  where spec != 'KeyGeneratorSpec'")
nrow(bench03cc)

```



## Ground Truth (MOP)

```{r}
tp <- gt[gt$vulnerability == "True",]
tn <- gt[gt$vulnerability == "False",]

sqldf("select count(distinct className) from tp")
sqldf("select count(distinct className) from tn")

# compute true positive 

mop_tp <- sqldf("select count(distinct className) as tp
                 from bench03mop 
                 where className in (select className from tp)")

# compute false positive 

mop_fp <- sqldf("select count(distinct className) as fp
                 from bench03mop 
                 where className in (select className from tn)")



# compute false-negative  

mop_fn <- sqldf("select count(distinct className) as fn
                 from tp 
                 where className not in (select className from bench03mop)")

# MOP true positives
mop_tp

# MOP false positives
mop_fp

# MOP false negatives
mop_fn

precision_mop <- mop_tp$tp / (mop_tp$tp + mop_fp$fp)
precision_mop

recall_mop <- mop_tp$tp / (mop_tp$tp + mop_fn$fn)
recall_mop
```

## Ground Truth 

```{r}
tp <- gt[gt$vulnerability == "True",]
tn <- gt[gt$vulnerability == "False",]

sqldf("select count(distinct className) from tp")
sqldf("select count(distinct className) from tn")
```

## Compute Precision and Recall (MOP)

```{r}

# compute true positive 

mop_tp <- sqldf("select count(distinct className) as tp
                 from bench03mop 
                 where className in (select className from tp)")

# compute false positive 

mop_fp <- sqldf("select count(distinct className) as fp
                 from bench03mop 
                 where className in (select className from tn)")



# compute false-negative  

mop_fn <- sqldf("select count(distinct className) as fn
                 from tp 
                 where className not in (select className from bench03mop)")

# MOP true positives
mop_tp

# MOP false positives
mop_fp

# MOP false negatives
mop_fn

precision_mop <- mop_tp$tp / (mop_tp$tp + mop_fp$fp)
precision_mop

recall_mop <- mop_tp$tp / (mop_tp$tp + mop_fn$fn)
recall_mop
```

## Compute Precision and Recall (CC)

```{r}

# compute true positive 

cc_tp <- sqldf("select count(distinct className) as tp
                 from bench03cc 
                 where className in (select className from tp)")

# compute false positive 

cc_fp <- sqldf("select count(distinct className) as fp
                 from bench03cc
                 where className in (select className from tn)")



# compute false-negative  

cc_fn <- sqldf("select count(distinct className) as fn
                 from tp 
                 where className not in (select className from bench03cc)")

# MOP true positives
cc_tp

# MOP false positives
cc_fp

# MOP false negatives
cc_fn

precision_cc <- cc_tp$tp / (cc_tp$tp + cc_fp$fp)
precision_cc

recall_cc <- cc_tp$tp / (cc_tp$tp + cc_fn$fn)
recall_cc
```


## Compute Precision and Recall (CG)

```{r}

# compute true positive 

cg_tp <- sqldf("select count(distinct className) as tp
                 from bench03cg
                 where className in (select className from tp)")

# compute false positive 

cg_fp <- sqldf("select count(distinct className) as fp
                 from bench03cg
                 where className in (select className from tn)")



# compute false-negative  

cg_fn <- sqldf("select count(distinct className) as fn
                 from tp 
                 where className not in (select className from bench03cg)")

# MOP true positives
cg_tp

# MOP false positives
cg_fp

# MOP false negatives
cg_fn

precision_cg <- cg_tp$tp / (cg_tp$tp + cg_fp$fp)
precision_cg

recall_cg <- cg_tp$tp / (cg_tp$tp + cg_fn$fn)
recall_cg
```
